---
title: "LAL6120-Outline/Schedule"
output: 
  html_document:
    includes:
      in_header: "favicon.html"
    theme: paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(repos = c(CRAN = "https://cloud.r-project.org/"))
install.packages("devtools")
devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
```

<style type="text/css">
  body{
  font-size: 12pt;
}
</style>

<style type="text/css">
.title {
  display: none;
}

#getting-started img {
  margin-right: 10px;
}

</style>

# **LAL 6120: Phonological and Phonetic Analysis**\
# *Sound Change*\
Instructor: [Chandan Narayan](https://ch-narayan.github.io)\
Course time: Wednesdays 11:30-3:30pm, Ross S803\
A print version of this syllabus is available here: [LING2200syllabus](LING2200syllabus.pdf)

## Outline/Syllabus

***

## Seminar description:
This graduate seminar will be a rigourous introduction to the topic of sound change. We will survey the intellectual history of formal approaches in the sound change literature. The course presupposes your having some background exposure to basic principles in phonetics (articulatory and acoustic) and phonology (nothing overly theoretical). We will focus on acoustics and speech perception explanations in sound change, but also consider sociological and extra-linguistic forces affecting change. While much of the sound change literature (especially pre-1960s) sought to describe the *what* of sound change, I want our focus to be on the *why* (and to some extent *how*) of sound change.

Students will be required to present readings and lead discussion. Final projects will address some problem in sound change of interest to the student.

## Seminar prerequisites:
This seminar is for first year graduate students in LAL. To that extent, the readings and discussion (and ultimately the work you produce) will reflect your background in Lingusitics, and phonetics and phonology in particular. I request that you contact me immediately if you do not have much background (i.e., intro courses in P&P), in which case we'll have some work to do outside of class. 

## Learning outcomes:

1. Demonstrate knowledge of theoretical approaches to sound change
2. Demonstrate the ability to sketch out a theoretically motivated approach to your own problem in sound change
3. Demonstrate ability to work within a team on a speech perception and acoustics project

## Evaluation

Your grade in the course will be determined by your performance on the following:

* 50% in class participation (including presenting readings)
* 50% contribution to collaborative class project

## Course text and readings
The readings will be provided in pdf form under the [Readings](Readings.html) tab. In some cases we may have to read texts where there isn't an electronic copy available. Library links will be provided in those cases.

### Class structure
We will go over the week's papers and outline strategies for our [collaborative class project](Proto-Greek.html).

### Email policy
Email me, but sometimes it may take a day for me to get back to you.

## Grading
York University uses a grading system detailed [here](http://calendars.registrar.yorku.ca/2012-2013/academic/grades/). Please familiarize yourself with it.

## Academic Honesty and Integrity
York students are required to maintain high standards of academic integrity and are subject to the Senate Policy on Academic Honesty. Please review the documents available [here](https://www.yorku.ca/secretariat/policies/policies/academic-honesty-senate-policy-on/). Academic offences are treated very seriously, and the disciplinary procedures are described there as well. Please consult the code if you have any question about the nature of academic offences and their penalties.

## Schedule

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
install.packages("kableExtra")

# For dev version
schedule <- read.csv("schedule.csv")
kable(schedule)
```


Week 1: Introduction, Meet and Greet, Assign reading presentations, Introduce collaborative project

Week 2 (History): de Courtenay (1910), Sievers (1901), PROJECT-

Week 3 (Modern theories): Ohala (1981), Lindblom (1990), Lindblom et al. (1995)

Week 4 (Salience and contrast): Liljencrants and Lindblom (1972), Flemming (2005), Narayan (2008)
